experDesign: stratifying samples into batches with minimal bias

### 2021-09-27 README.Rmd

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/experDesign)](https://CRAN.R-project.org/package=experDesign)
[![R build status](https://github.com/llrs/experDesign/workflows/R-CMD-check/badge.svg)](https://github.com/llrs/experDesign/actions?workflow=R-CMD-check)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/llrs/experDesign?branch=master&svg=true)](https://ci.appveyor.com/project/llrs/experDesign)
[![Travis build status](https://travis-ci.org/llrs/experDesign.svg?branch=master)](https://travis-ci.org/llrs/experDesign)
[![Coverage status](https://codecov.io/gh/llrs/experDesign/branch/master/graph/badge.svg)](https://codecov.io/github/llrs/experDesign?branch=master)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/experDesign)](https://CRAN.R-project.org/package=experDesign)
[![R build status](https://github.com/llrs/experDesign/workflows/R-CMD-check/badge.svg)](https://github.com/llrs/experDesign/actions?workflow=R-CMD-check)
[![Coverage status](https://codecov.io/gh/llrs/experDesign/branch/master/graph/badge.svg)](https://codecov.io/github/llrs/experDesign?branch=master)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->
